treats manual

### 2023-12-06 inst/gitbook/02_make.traits.Rmd
book up

>>>>

### Quick overview

function | arguments | input | what does it do
---------|-----------|-------|----------------
`make.traits` | process* | a function | simulates the trait (see below)
`make.traits` | n | a numeric value | the number of dimensions
`make.traits` | start | one or more numeric values | the starting values for each dimensions
`make.traits` | process.args | ... | anything to be passed to `process` (see below)
`make.traits` | trait.names | a character string | the name(s) of the trait(s)
`make.traits` | add | a `treats` object | another trait generated by `make.traits`
`make.traits` | update | a `treats` object | another trait generated by `make.traits`
`make.traits` | test | logical | whether to test the validity of the trait
`make.traits` | background | a `treats` object | another trait generated by `make.traits` (to run in the background)
---------|-----------|-------|----------------
`process` | x0 | a numeric value | the value of the previous trait
`process` | edge.length | a numeric value | the branch length value
`process` | ... | ... | any other argument to be handled by the process

\* non-optional arguments

### 2023-12-06 inst/gitbook/03_make.modifiers.Rmd
book up

>>>>

### Quick overview

function | arguments | input | what does it do
---------|-----------|-------|----------------
`make.modifiers` | branch.length | a function | generating branch length (see below)
`make.modifiers` | selection | a function | selecting a lineage (see below)
`make.modifiers` | speciation | a function | choosing between speciation and extinction (see below)
`make.modifiers` | condition | a function | a function that affects the condition of when to trigger the functions above (see below)
`make.modifiers` | modify | a function | a function that modifies the value of the trigger value generated when the `condition` is met (see below)
`make.modifiers` | add | a `treats` object | another modifier generated by `make.modifiers`
`make.modifiers` | update | a `treats` object | another modifier generated by `make.modifiers`
`make.modifiers` | test | logical | whether to test the validity of the modifier
---------|-----------|-------|----------------
`branch.length`, `selection`, `speciation`, `condition` | bd.params | a `treats` object generated by `make.bd.params` | usually handled internally (contains the either the birth-death values or their distribution)
... | lineage | a named "lineage" list | usually handled internally (contains the current state of the simulations)
... | trait.values | a matrix | usually handled internally (contains the current generated traits of the simulations)

### 2023-12-06 inst/gitbook/04_make.events.Rmd
book up

function | arguments | input | what does it do
---------|-----------|-------|----------------
`make.events` | target* | any of the following: "taxa", "bd.params", "traits", "modifiers" or "founding" | what aspect of the simulation should the event target
 | condition* | a function | a function that affects the condition of when to trigger the event (see below)
 | modification* | a function | a function that applies the modification to the target if the condition is triggered (see below)
 | add | a `treats` object | another event generated by `make.events`
 | test | logical | whether to test the validity of the event
 | event.name | a character string | the name of the event
 | replications | a number | if possible how many times is the event allowing to be repeated
 | additional.args | ... | any additional arguments to be passed to the event

@@

function | arguments | input | what does it do
---------|-----------|-------|----------------
`age.condition`, `taxa.condition`, `trait.condition` | x | the value to check the target against | e.g. time = x, taxa = x or trait = x (see below)
 | condition | a relational operator | e.g. `==`, `>`, `!=`, etc. for asking for example `time == x` 
 | ... | any additional arguments to be passed to the event | |

@@

 function | arguments | input | what does it do
---------|-----------|-------|----------------
random.extinction | x | a numeric value | the proportion of species to make extinct
trait.extinction | x | a numeric value | the trait value when to trigger the extinction
 | condition | a relational operator | the relation to the trait value (e.g. `x = 1` and `condition =  >` makes species that have a trait value > 1 go extinct)
bd.params.update | ... | any argument to be passed to `make.bd.params` | |
traits.update | ... | any argument to be passed to `make.traits` | |
modifiers.update | ... | any argument to be passed to `make.modifiers` | |

>>>>

function | arguments | input | what does it do
---------|-----------|-------|----------------
`make.events` | target* | any of the following: "taxa", "bd.params", "traits", "modifiers" or "founding" | what aspect of the simulation should the event target
`make.events` | condition* | a function | a function that affects the condition of when to trigger the event (see below)
`make.events` | modification* | a function | a function that applies the modification to the target if the condition is triggered (see below)
`make.events` | add | a `treats` object | another event generated by `make.events`
`make.events` | test | logical | whether to test the validity of the event
`make.events` | event.name | a character string | the name of the event
`make.events` | replications | a number | if possible how many times is the event allowing to be repeated
`make.events` | additional.args | ... | any additional arguments to be passed to the event

@@

function | arguments | input | what does it do
---------|-----------|-------|----------------
`age.condition`, `taxa.condition`, `trait.condition` | x | the value to check the target against | e.g. time = x, taxa = x or trait = x (see below)
... | condition | a relational operator | e.g. `==`, `>`, `!=`, etc. for asking for example `time == x` 
... | ... | any additional arguments to be passed to the event | |

@@

 function | arguments | input | what does it do
---------|-----------|-------|----------------
`random.extinction` | x | a numeric value | the proportion of species to make extinct
`trait.extinction` | x | a numeric value | the trait value when to trigger the extinction
`trait.extinction` | condition | a relational operator | the relation to the trait value (e.g. `x = 1` and `condition =  >` makes species that have a trait value > 1 go extinct)
`bd.params.update` | ... | any argument to be passed to `make.bd.params` | |
`traits.update` | ... | any argument to be passed to `make.traits` | |
`modifiers.update` | ... | any argument to be passed to `make.modifiers` | |

### 2023-12-06 inst/gitbook/_book/treats_manual.tex
book up

\title{treats manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-11-22}

@@

\strut

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x559776bed260>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x559775650390>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x559775658740>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) <= (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x559775657e10>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
target*\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any of the following: ``taxa'', ``bd.params'', ``traits'', ``modifiers'' or ``founding''\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
what aspect of the simulation should the event target\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
condition*\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a function\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a function that affects the condition of when to trigger the event (see below)\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
modification*\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a function\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a function that applies the modification to the target if the condition is triggered (see below)\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
add\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a \texttt{treats} object\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
another event generated by \texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
test\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
logical\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
whether to test the validity of the event\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
event.name\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a character string\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
the name of the event\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
replications\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a number\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
if possible how many times is the event allowing to be repeated\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
additional.args\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any additional arguments to be passed to the event\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{age.condition}, \texttt{taxa.condition}, \texttt{trait.condition}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
the value to check the target against\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
e.g.~time = x, taxa = x or trait = x (see below)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
condition\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a relational operator\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
e.g.~\texttt{==}, \texttt{\textgreater{}}, \texttt{!=}, etc. for asking for example \texttt{time\ ==\ x}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
any additional arguments to be passed to the event\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
random.extinction\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a numeric value\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the proportion of species to make extinct\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
trait.extinction\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a numeric value\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the trait value when to trigger the extinction\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
condition\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
a relational operator\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
the relation to the trait value (e.g.~\texttt{x\ =\ 1} and \texttt{condition\ =\ \ \textgreater{}} makes species that have a trait value \textgreater{} 1 go extinct)\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
bd.params.update\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.bd.params}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
traits.update\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.traits}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
modifiers.update\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.modifiers}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpqXtl0Y/file8c965577e651}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpqXtl0Y/file8c9618f635d6}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpqXtl0Y/file8c9623bb5976}

>>>>

\title{treats manual}
\author{Thomas Guillerme (\href{mailto:guillert@tcd.ie}{\nolinkurl{guillert@tcd.ie}})}
\date{2023-12-06}

@@

@@

\begin{verbatim}
## $main
## $main$A
## $main$A$process
## function (x0 = 0, edge.length = 1, Sigma = diag(length(x0)), 
##     ...) 
## {
##     return(t(MASS::mvrnorm(n = 1, mu = x0, Sigma = Sigma * edge.length, 
##         ...)))
## }
## <bytecode: 0x55e979290a30>
## <environment: namespace:treats>
## 
## $main$A$start
## [1] 0
## 
## $main$A$trait_id
## [1] 1
## 
## 
## 
## $background
## NULL
\end{verbatim}

@@

\begin{verbatim}
## $waiting
## $waiting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(rexp(1, sum(lineage$n * (bd.params$speciation + bd.params$extinction))))
## }
## <bytecode: 0x55e977cfc060>
## <environment: namespace:treats>
## 
## $waiting$internal
## NULL
## 
## 
## $selecting
## $selecting$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(sample(lineage$n, 1))
## }
## <bytecode: 0x55e977d04410>
## <environment: namespace:treats>
## 
## $selecting$internal
## NULL
## 
## 
## $speciating
## $speciating$fun
## function (bd.params, lineage = NULL, trait.values = NULL, modify.fun = NULL) 
## {
##     return(runif(1) <= (bd.params$speciation/(bd.params$speciation + 
##         bd.params$extinction)))
## }
## <bytecode: 0x55e977d03ae0>
## <environment: namespace:treats>
## 
## $speciating$internal
## NULL
## 
## 
## $call
## $call$waiting
## $call$waiting$fun
## [1] "default"
## 
## 
## $call$selecting
## $call$selecting$fun
## [1] "default"
## 
## 
## $call$speciating
## $call$speciating$fun
## [1] "default"
\end{verbatim}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
target*\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any of the following: ``taxa'', ``bd.params'', ``traits'', ``modifiers'' or ``founding''\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
what aspect of the simulation should the event target\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
condition*\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a function\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
a function that affects the condition of when to trigger the event (see below)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
modification*\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a function\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
a function that applies the modification to the target if the condition is triggered (see below)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
add\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a \texttt{treats} object\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
another event generated by \texttt{make.events}\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
test\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
logical\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
whether to test the validity of the event\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
event.name\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a character string\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the name of the event\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
replications\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a number\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
if possible how many times is the event allowing to be repeated\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{make.events}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
additional.args\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
any additional arguments to be passed to the event\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{age.condition}, \texttt{taxa.condition}, \texttt{trait.condition}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
the value to check the target against\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
e.g.~time = x, taxa = x or trait = x (see below)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
condition\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a relational operator\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
e.g.~\texttt{==}, \texttt{\textgreater{}}, \texttt{!=}, etc. for asking for example \texttt{time\ ==\ x}\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any additional arguments to be passed to the event\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
function\strut
\end{minipage} & \begin{minipage}[b]{0.23\columnwidth}\raggedright
arguments\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedright
input\strut
\end{minipage} & \begin{minipage}[b]{0.33\columnwidth}\raggedright
what does it do\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{random.extinction}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a numeric value\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the proportion of species to make extinct\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{trait.extinction}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
x\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a numeric value\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the trait value when to trigger the extinction\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{trait.extinction}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
condition\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
a relational operator\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
the relation to the trait value (e.g.~\texttt{x\ =\ 1} and \texttt{condition\ =\ \ \textgreater{}} makes species that have a trait value \textgreater{} 1 go extinct)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{bd.params.update}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.bd.params}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{traits.update}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.traits}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
\texttt{modifiers.update}\strut
\end{minipage} & \begin{minipage}[t]{0.23\columnwidth}\raggedright
\ldots{}\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedright
any argument to be passed to \texttt{make.modifiers}\strut
\end{minipage} & \begin{minipage}[t]{0.33\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f6e0175d3}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f7aec27f9}

@@

\includegraphics[width=6.5in]{../../../../../../tmp/RtmpMmzXjr/file3e7f5c6b6ac6}
